---
title: "PvSeroTaT Serological Assay Quality Control Report"
date: "`r Sys.Date()`"
output: 
  html_document: 
    theme: cosmo
    code_folding: hide
params:
  raw_data_filename: NA
  experiment_name: NA
  experiment_notes: NA
  platform: NA
  date: NA
  stdcurve_plot: NA
  plateqc_plot: NA
  check_repeats_table: NA
  blanks_plot: NA
  model_plot: NA
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = FALSE, message = FALSE, tidy = TRUE)
require(tidyverse)
require(readxl)
require(drc)
require(here)
```

***
### QC Report for experiment: `r params$experiment_name` analysed on `r params$date`{.tabset}
***

#### Plot of Standard Curves

```{r standard curves plot}
params$stdcurve_plot
```

#### Plot of Model Results

```{r model results plot}
model_plot <- params$model_plot

for (plot_name in names(model_plot)) {
  print(plot_name)
}
```

#### Plot of Bead Counts

Any wells with < 15 beads/well are indicated in red, and should be double-checked manually.

```{r bead counts plot}
params$plateqc_plot
#params$check_repeats_table
```

#### Plot of Blank Samples

Blank samples should record MFI<50 for each protein. If any proteins are above the dashed line, they should be double-checked manually.

```{r blank samples plot}
params$blanks_plot
```

#### Experiment Information

**Experiment Notes:** `r params$experiment_notes`

**Platform Chosen**: `r params$platform``

**Raw Data Filename/s:** `r params$raw_data_filename`